---
title: "Data Management and Stats Desc"
author: "Anna Alari"
date: "4/4/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message=FALSE)
```


```{r, echo=FALSE, warning = FALSE, message=FALSE}
library(xlsx)
library(Hmisc)
library(lubridate)
library(effects)
library(ggplot2)
library(prettyR)
library(segmented)
library(ggeffects)
library(devtools)
library(zoo)
library(knitr)
library(kableExtra)
library(tidyverse)
library("writexl")
library(hrbrthemes)
library(tidyverse)
library(ggridges)
library(viridis)
library(ggpubr)
library(R.utils)
library(meta)
library(jtools)
library(huxtable)
```

I create the database by merging data from CEPEM project and data from CEPIDC: 

```{r, warning = FALSE}
# I load the final data

load("C:/Users/aalari/Dropbox/Noemie/FInal Analysis - SpF + CepiDC/villes_s.RData")

```


## Summary Statistics for Mortality during summer period

```{r, echo=FALSE}
varbl<-c("Dates", "Zone", "cv_tot","respi_tot","tempmin","tempmax","tempmoy","heat_wave", "mois")

villes_sub<-lapply(villes_s,function(x){x[,varbl]})

data<-rbind(villes_sub[["avignon"]],villes_sub[["BM"]], villes_sub[["bordeaux"]],villes_sub[["clermont"]],villes_sub[["dijon"]],villes_sub[["grenoble"]], villes_sub[["lehavre"]], villes_sub[["lille"]],villes_sub[["lyon"]],villes_sub[["marseille"]],villes_sub[["montpellier"]],villes_sub[["nancy"]],villes_sub[["nantes"]],villes_sub[["nice"]],villes_sub[["paris"]],villes_sub[["rennes"]],villes_sub[["rouen"]],villes_sub[["saint_etienne"]],villes_sub[["strasbourg"]],villes_sub[["toulon"]],villes_sub[["toulouse"]])


data <- data %>% group_by(Zone)

data <- data %>% filter(mois %in% c("6","7","8"))
```

```{r, echo=FALSE}
library(gdata)

levels(data$Zone)
data$Zone<-as.factor(as.character(data$Zone))

order<-c("bordeaux","lehavre","ntes","rennes","rouen","clermont","dijon","grenoble","lyon","ncy","saint-etienne", "strasbourg","bm","lille", "paris","toulouse","avignon","marseille","montpellier","nice","toulon")

data$Zone <- reorder.factor(data$Zone, new.order=order)

levels(data$Zone)

data$Zone<-factor(data$Zone,levels(data$Zone), labels=c("Bordeaux","Le Havre","Nantes","Rennes","Rouen","Clermont-Ferrant","Dijon","Grenoble","Lyon","Nancy","Saint-Etienne", "Strasbourg","Douai-Lens","Lille", "Paris","Toulouse","Avignon","Marseille","Montpellier","Nice","Toulon")) 

order<-c("Bordeaux","Le Havre","Nantes","Rennes","Rouen","Clermont-Ferrant","Dijon","Grenoble","Lyon","Nancy","Saint-Etienne", "Strasbourg","Douai-Lens","Lille", "Paris","Toulouse","Avignon","Marseille","Montpellier","Nice","Toulon")

levels(data$Zone)

```

```{r, echo=FALSE}
tabmort<-data %>% summarise(
  'Min Cv'=min(cv_tot,na.rm=TRUE),
  'Mean Cv'=mean(cv_tot,na.rm=TRUE),
  'Max Cv'=max(cv_tot,na.rm=TRUE),
  'Min Respi'=min(respi_tot,na.rm=TRUE),
  'Mean Respi'=mean(respi_tot,na.rm=TRUE),
  'Max Respi'=max(respi_tot,na.rm=TRUE),
    )

tabmort %>% kable(caption = "Mortality per City") %>% kable_styling(bootstrap_options = c("hover", "condensed","bordered"),full_width = F)%>% add_header_above(c(" ", "Cardiovascual Causes" = 3, "Respiratory causes"=3))%>%
  column_spec(1, bold = T, border_right = T)%>%
  column_spec(4, border_right = T)
```
\  
\  

Heat waves episodes in 20 different cities in French during the period going from 2000 to 2015 were identified: 

```{r, echo=FALSE}
N_HeatWave<-matrix(NA,nrow = 21,ncol=4)
colnames(N_HeatWave)<-c("city","June","July","August")
N_HeatWave[,1]<-names(villes_s)

for (i in (1:length(villes_s))){
N_HeatWave[i,2:4]<-as.numeric(t(villes_s [[i]]%>% group_by(mois)%>% summarise(
  N_HeatWave = sum(heat_wave)))[2,])
}  
N_HeatWave%>% kable(caption = "Number of Heat Waves per city and per Month, 2000-2015")%>% kable_styling(bootstrap_options = c("hover", "condensed","bordered"),full_width = F)
  
```
\  
\  


### Mortality during summer period for non heat wave days and for heat wave days

#### *Cardiovascular Mortality*

```{r,echo=FALSE,warning=FALSE, fig.dim = c(8, 8)}

data$heat_wave<-as.factor(as.character(data$heat_wave))

data <- data %>% group_by(heat_wave,Zone)

ggplot(data, aes(x="", y=cv_tot, fill=heat_wave)) + 
    geom_boxplot() + xlab("")+ ylab("Cardiovascular Deaths")+ 
  labs(x = "") +
    facet_wrap(~Zone, scale="free") + scale_fill_manual(values=c("cyan3", "coral1")) 

```
\  
\  

#### *Respiratory Mortality*

```{r,echo=FALSE,warning=FALSE, fig.dim = c(8, 8)}

ggplot(data, aes(x="", y=respi_tot, fill=heat_wave)) + 
    geom_boxplot() + xlab("")+ ylab("Respiratory Deaths")+ 
  labs(x = "") +
    facet_wrap(~Zone, scale="free")+ scale_fill_manual(values=c("cyan3", "coral1"))

```



## Summary Statistics for Temperature during summer period



### Average Temperature Distribution during summer period

```{r, fig.width=8, fig.height=8, fig.align = "center", echo=FALSE}
data$Zone <- reorder.factor(data$Zone, new.order=rev(order))

ggplot(data, aes(x = tempmoy, y = Zone, fill=..x..)) +
  geom_density_ridges_gradient(scale = 3, rel_min_height = 0.01) +
  scale_fill_viridis(option = "B") + xlab("Temperature [°C]") + 
  ylab("Urban Agglomeration") +
  theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    )
```

## Descriptive Statistics

```{r}
data<-data %>% ungroup()
data<-data %>% group_by(Zone)

data$Zone <- reorder.factor(data$Zone, new.order=order)

tabdesc<-data %>% summarise(
  'Temp 25 Perc'=quantile(tempmoy, na.rm=TRUE)[2],
  'Median Temp'=median(tempmoy, na.rm=TRUE),
  'Temp 75 Perc'=quantile(tempmoy, na.rm=TRUE)[4],
      )

tabdesc[,2:4]<-round(tabdesc[,2:4],digits = 2)
tabdesc %>% kable(caption = "Average Temperature statistics per City during summer period") %>% kable_styling(bootstrap_options = c("hover", "condensed","bordered"),full_width = F)%>% add_header_above(c(" ", "Average Temperature" = 3))%>%
  column_spec(1, bold = T, border_right = T)%>%
  column_spec(4, border_right = T)
```

