
---
title: "Effect of different Heat wave timing on cardiovascular mortality in France with DLNM"
author: "Anna Alari and Noemie Letellier"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE)
```


```{r, echo=FALSE, warning = FALSE, message=FALSE}
library(xlsx)
library(Hmisc)
library(lubridate)
library(effects)
library(ggplot2)
library(prettyR)
library(segmented)
library(splines)
library(mgcViz)
library(ggeffects)
library(devtools)
library(zoo)
library(mvmeta)
library(dlnm)
library(knitr)
library(kableExtra)
library(tidyverse)
library("writexl")
library(metafor)
library(forestplot)
library("writexl")
library(hrbrthemes)
library(tidyverse)
library(ggridges)
library(viridis)
library(ggpubr)
library(R.utils)
library(meta)
library(jtools)
library(huxtable)

load("C:/Users/aalari/Dropbox/Noemie/FInal Analysis - SpF + CepiDC/villes_s.RData")

```



```{r, echo=FALSE}
# 1. SPECIFICATION PARAMETERS OF THE EXPOSURE-RESPONSE DIMENSION OF THE CROSS-BASIS
names(villes_s)[2]<-"douai-lens"
mft <-lapply(villes_s,function(x){median(x$tempmoy,na.rm=TRUE)}) 
```



## 1. FIRST STAGE ANALYSIS: Estimation of the exposure-response associations at city level for 2 periods of the summer

I decided to exclude the months of may and September, when extreme heat event never happen in France. 
Then I define two periods of the summer:  
- 1st part of the summer: 1st of june until 15th of July
- 2nd part of the summer: From 16th of July until end of August


```{r}

# Create an database for each period
summer1<-list()
summer2<-list()


for (i in 1:length(villes_s)){
  summer1[[i]]<-villes_s[[i]][which(villes_s[[i]]$day > 31 & villes_s[[i]]$day<77),]
  summer1[[i]]$time<-1:nrow(summer1[[i]])
  summer2[[i]]<-villes_s[[i]][which(villes_s[[i]]$day > 76 & villes_s[[i]]$day<124),]
  summer2[[i]]$time<-1:nrow(summer2[[i]])
  }

names(summer1)<-names(villes_s)
names(summer2)<-names(villes_s)

```


#### Defintion of the cross-basis function (with its two dimensions) for the temperature of each month:

```{r}
# 1. SPECIFICATION PARAMETERS OF THE EXPOSURE-RESPONSE DIMENSION OF THE CROSS-BASIS

argvar_summer<-list()

for (i in 1: length(villes_s)){
argvar_summer[[i]] <- list(fun="ns", knots = quantile(villes_s[[i]]$tempmoy,c(50,90)/100, na.rm=T),
  Bound=range(villes_s[[i]]$tempmoy,na.rm=T))
}

names(argvar_summer)<-names(villes_s)

# 2. SPECIFICATION PARAMETERS OF THE LAG-ASSOCIATION DIMENSION OF THE CROSS-BASIS
# Definition of the maximum lag: I chose 7 days
maxlag <- 5

arglag <- list(fun="ns",knots=logknots(maxlag,nk=2))

# - CREATE CROSSBASIS OBJECTS
cb_summer1<-list()
cb_summer2<-list()

for (i in 1: length(villes_s)){
cb_summer1[[i]] <- crossbasis(summer1[[i]]$tempmoy,maxlag,argvar_summer[[i]],arglag, group=summer1[[i]]$year)  
cb_summer2[[i]] <- crossbasis(summer2[[i]]$tempmoy,maxlag,argvar_summer[[i]],arglag, group=summer2[[i]]$year)  
}

names(cb_summer1)<-names(villes_s)
names(cb_summer2)<-names(villes_s)
```

#### Fit the models for each city and each period for CARDIOVASCULAR DEATHS
Include in the models the crossbasis term of temperature, along with the indicator for day of the week (Jours), bank holidays (Vacances) and natural cubic spline of time with 8 df per year.

```{r}
mod_summer1<-list()
mod_summer2<-list()

for (i in 1: length(villes_s)){
cb_func1<-cb_summer1[[i]]
mod_summer1[[i]] <- glm(cv_tot ~ cb_func1 + Jours + ns(day, 4) + ns(time,3), data=summer1[[i]], family=quasipoisson)
cb_func2<-cb_summer2[[i]]
mod_summer2[[i]] <- glm(cv_tot ~ cb_func2 + Jours + ns(day, 4) + ns(time,3), data=summer2[[i]], family=quasipoisson)
}

```
### Get predictions for each model centering on median value:

```{r}
pred_summer1<-list()
pred_summer2<-list()

for (i in 1: length(villes_s)){
  pred_summer1[[i]] <- crosspred(cb_func1, mod_summer1[[i]],cen=mft[[i]], by=1)
  pred_summer2[[i]] <- crosspred(cb_func2, mod_summer2[[i]],cen=mft[[i]], by=1)
  }
```


### Plot of OVERALL curves WITH DIFFERENT FUNCTION FOR EACH PERIOD, in each location

We compare the different shapes of the cumulative exposure-response association (in terms of relative risks (RR) and centered in the mft) across the 7 days of lag, estimated for each period of the summer

```{r, echo = FALSE}
xlab <- expression(paste("Temperature (˚C)"))


layout(matrix(c(1,2,3,4,5,6),ncol=3,nrow=2,byrow=T))
par(mar=c(5,4,3,1),mgp=c(3,1,0),las=1,cex.axis=0.9,cex.lab=1)
for (i in 1:6){
plot(pred_summer1[[i]],"overall",col="blue",axes=T,lab=c(6,5,7), xlab=xlab,
  ylab="RR", ci.arg=list(density=20,angle=-45,col=4), main=names(villes_s)[i])
lines(pred_summer2[[i]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")
}

layout(matrix(c(1,2,3,4,5,6),ncol=3,nrow=2,byrow=T))
par(mar=c(5,4,3,1),mgp=c(3,1,0),las=1,cex.axis=0.9,cex.lab=1)
plot(pred_summer1[[7]],"overall",col="blue",axes=T,lab=c(6,5,7), ylim=c(0,4), xlab=xlab,
  ylab="RR", ci.arg=list(density=20,angle=-45,col=4), main=names(villes_s)[7])
lines(pred_summer2[[7]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")
for (i in 8:12){
#par(mar=c(5,4,3,1),mgp=c(3,1,0),las=1,cex.axis=0.9,cex.lab=1)
plot(pred_summer1[[i]],"overall",col="blue",axes=T,lab=c(6,5,7), xlab=xlab,
  ylab="RR", ci.arg=list(density=20,angle=-45,col=4), main=names(villes_s)[i])
lines(pred_summer2[[i]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")
}
layout(matrix(c(1,2,3,4,5,6),ncol=3,nrow=2,byrow=T))
for (i in 13:15){
par(mar=c(5,4,3,1),mgp=c(3,1,0),las=1,cex.axis=0.9,cex.lab=1)
plot(pred_summer1[[i]],"overall",col="blue",axes=T,lab=c(6,5,7),xlab=xlab,
  ylab="RR", ci.arg=list(density=20,angle=-45,col=4), main=names(villes_s)[i])
lines(pred_summer2[[i]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")
}
par(mar=c(5,4,3,1),mgp=c(3,1,0),las=1,cex.axis=0.9,cex.lab=1)
plot(pred_summer1[[16]],"overall",col="blue",axes=T,lab=c(6,5,7),xlab=xlab,
  ylab="RR", ci.arg=list(density=20,angle=-45,col=4), ylim=c(0, 4), main=names(villes_s)[16])
lines(pred_summer2[[16]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")
for (i in 17:18){
par(mar=c(5,4,3,1),mgp=c(3,1,0),las=1,cex.axis=0.9,cex.lab=1)
plot(pred_summer1[[i]],"overall",col="blue",axes=T,lab=c(6,5,7),xlab=xlab,
  ylab="RR", ci.arg=list(density=20,angle=-45,col=4), main=names(villes_s)[i])
lines(pred_summer2[[i]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")
}

layout(matrix(c(1,2,3,4,5,6),ncol=3,nrow=2,byrow=T))
for (i in 19:21){
par(mar=c(5,4,3,1),mgp=c(3,1,0),las=1,cex.axis=0.9,cex.lab=1)
plot(pred_summer1[[i]],"overall",col="blue",axes=T,lab=c(6,5,7),xlab=xlab,
  ylab="RR", main=names(villes_s)[i], ci.arg=list(density=20,angle=-45,col=4))
lines(pred_summer2[[i]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")
}
```

## 2. Second stage analysis to obtain pooled estimates

The set of 20 coefficients of the cross-basis in each city are then reduced. We reduce the fit of a bi-dimensional DLNM to summaries expressed by parameters of one-dimensional basis. 

```{r}
####################################################################
# BUILT OBJECTS WHERE RESULTS WILL BE STORED
#   y- IS THE MATRIX FOR THE OUTCOME PARAMETERS
#   S- IS THE LISTS OF (CO)VARIANCE MATRICES

# OVERALL CUMULATIVE SUMMARIES
yall1 <- matrix(NA,length(villes_s),3,dimnames=list(names(villes_s),paste("b",seq(3),sep="")))
yall2 <- matrix(NA,length(villes_s),3,dimnames=list(names(villes_s),paste("b",seq(3),sep="")))

# (CO)VARIANCE MATRICES
cov1 <- vector("list",length(villes_s))
cov2 <- vector("list",length(villes_s))

names(cov1)<-names(cov2) <- names(villes_s)




for (i in 1: length(villes_s)){
    cb_func1<-cb_summer1[[i]]
    red_par1 <- crossreduce(cb_func1,mod_summer1[[i]], cen=mft[[i]])
    yall1[i,] <- coef(red_par1)  #I STORE THE RESULTS for the OVERALL CUMULATIVE SUMMARY FOR THE MAIN MODEL
    cov1[[i]] <- vcov(red_par1)  # I store the covariance matrix
    cb_func2<-cb_summer2[[i]]
    red_par2 <- crossreduce(cb_func2,mod_summer2[[i]], cen=mft[[i]])
    yall2[i,] <- coef(red_par2)
    cov2[[i]] <- vcov(red_par2)
    }




```

For each city we derive the vector with 4 reduced parameters of the natural spline of temperature for the overall cumulative summary association. 


Then we: 

- 2a. RUN THE MULTIVARIATE META-ANALYTICAL MODELS WITH mvmeta
- 2b. Obtain BLUP predictions for each location
- 2c. CREATE BASIS VARIABLES USING onebasis, TO BE USED FOR PREDICTION
- 2d. OBTAIN PREDICTIONS THROUGH crosspred (dlnm)


### 2a. META-ANALYTICAL MODELS:

```{r}
library(mvmeta)
library(mixmeta)

# OVERALL CUMULATIVE SUMMARY FOR THE MAIN MODEL
mvall1 <- mvmeta(yall1,cov1, method="ml")
mvall2 <- mvmeta(yall2,cov2,method="ml")

summary(mvall1)
summary(mvall2)
```

### 2b. BLUP PREDICTIONS for each city


```{r}
blup1<-blup(mvall1, vcov=T)
blup2<-blup(mvall2, vcov=T)

```



```{r}
# CREATE BASES FOR PREDICTION

# BASES OF TEMPERATURE AND LAG USED TO PREDICT, EQUAL TO THAT USED FOR ESTIMATION
# COMPUTED USING THE ATTRIBUTES OF THE CROSS-BASIS USED IN ESTIMATION

x<-lapply(villes_s,function(x){x[,"tempmoy"]})
tempall<-rbind(x[["avignon"]],x[["douai-lens"]],x[["bordeaux"]],x[["clermont"]],x[["dijon"]],x[["grenoble"]], x[["lehavre"]], x[["lille"]],x[["lyon"]],x[["marseille"]], x[["montpellier"]],x[["nancy"]],x[["nantes"]],x[["nice"]],x[["paris"]],x[["rennes"]],x[["rouen"]],x[["saint_etienne"]],x[["strasbourg"]],x[["toulon"]],x[["toulouse"]])

x_1<-lapply(summer1,function(x){x[,"tempmoy"]})
tempall_1<-rbind(x_1[["avignon"]],x_1[["douai-lens"]],x_1[["bordeaux"]],x_1[["clermont"]],x_1[["dijon"]],x_1[["grenoble"]], x_1[["lehavre"]], x_1[["lille"]],x_1[["lyon"]],x_1[["marseille"]], x_1[["montpellier"]],x_1[["nancy"]],x_1[["nantes"]],x_1[["nice"]],x_1[["paris"]],x_1[["rennes"]],x_1[["rouen"]],x_1[["saint_etienne"]],x_1[["strasbourg"]],x_1[["toulon"]],x_1[["toulouse"]])

x_2<-lapply(summer2,function(x){x[,"tempmoy"]})
tempall_2<-rbind(x_2[["avignon"]],x_2[["douai-lens"]],x_2[["bordeaux"]],x_2[["clermont"]],x_2[["dijon"]],x_2[["grenoble"]], x_2[["lehavre"]], x_2[["lille"]],x_2[["lyon"]],x_2[["marseille"]], x_2[["montpellier"]],x_2[["nancy"]],x_2[["nantes"]],x_2[["nice"]],x_2[["paris"]],x_2[["rennes"]],x_2[["rouen"]],x_2[["saint_etienne"]],x_2[["strasbourg"]],x_2[["toulon"]],x_2[["toulouse"]])


# minimum<-min(data.frame(lapply(villes_s,function(x){min(x$tempmoy, na.rm=TRUE)})))
# maximum<-max(data.frame(lapply(villes_s,function(x){max(x$tempmoy, na.rm=TRUE)})))

xvar <- seq(min(tempall, na.rm=TRUE),max(tempall, na.rm=TRUE),by=0.1)
xvar_1 <- seq(min(tempall_1, na.rm=TRUE),max(tempall_1, na.rm=TRUE),by=0.1)
xvar_2 <- seq(min(tempall_2, na.rm=TRUE),max(tempall_2, na.rm=TRUE),by=0.1)

bvar <- onebasis(xvar, "ns", knots = quantile(tempall,c(50,90)/100, na.rm=T),
  Bound=range(tempall,na.rm=T))
bvar_1 <- onebasis(xvar_1, "ns", knots = quantile(tempall_1,c(50,90)/100, na.rm=T),
  Bound=range(tempall_1,na.rm=T))
bvar_2 <- onebasis(xvar_2, "ns", knots = quantile(tempall_2,c(50,90)/100, na.rm=T),
  Bound=range(tempall_2,na.rm=T))

cityall1 <- apply(yall1,1,function(x) exp(bvar_1%*%x))
cityall2 <- apply(yall2,1,function(x) exp(bvar_2%*%x))

####################################################################
```


```{r}
cityblp1<-list()
cityblp2<-list()

for (i in 1:length(villes_s)){
  
  cb_summer1 <- onebasis(summer1[[i]]$tempmoy, "ns", knots = quantile(summer1[[i]]$tempmoy,c(50,90)/100, na.rm=T),
  Bound=range(summer1[[i]]$tempmoy,na.rm=T))  
  cb_summer2 <- onebasis(summer2[[i]]$tempmoy, "ns", knots = quantile(summer2[[i]]$tempmoy,c(50,90)/100, na.rm=T),
  Bound=range(summer2[[i]]$tempmoy,na.rm=T))

 cityblp1[[i]] <- crosspred(cb_summer1, coef=blup1[[i]]$blup,vcov=blup1[[i]]$vcov, model.link="log",by=0.1,from=min(summer1[[i]]$tempmoy, na.rm=TRUE),to=max(summer1[[i]]$tempmoy, na.rm=TRUE), cen=median(summer1[[i]]$tempmoy, na.rm=TRUE))

 cityblp2[[i]] <- crosspred(cb_summer2, coef=blup2[[i]]$blup,vcov=blup2[[i]]$vcov, model.link="log",by=0.1,from=min(summer2[[i]]$tempmoy, na.rm=TRUE),to=max(summer2[[i]]$tempmoy, na.rm=TRUE), cen=median(summer2[[i]]$tempmoy, na.rm=TRUE))
}
```


```{r, echo = FALSE}

layout(matrix(c(1,2,3,4,5,6),ncol=3,nrow=2,byrow=T))
par(mar=c(5,4,3,1),mgp=c(3,1,0),las=1,cex.axis=0.9,cex.lab=1)
for (i in 1:4){
plot(cityblp1[[i]],col="blue",axes=T,lab=c(6,5,7), xlab=xlab,ylim=c(min(cityblp2[[i]]$allRRlow),max(cityblp2[[i]]$allRRhigh)),
  ylab="RR", ci.arg=list(density=20,angle=-45,col=4), main=names(villes_s)[i])
lines(cityblp2[[i]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")
}
for (i in 5:6){
plot(cityblp1[[i]],col="blue",axes=T,lab=c(6,5,7), xlab=xlab,ylim=c(min(cityblp2[[i]]$allRRlow),3),
  ylab="RR", ci.arg=list(density=20,angle=-45,col=4), main=names(villes_s)[i])
lines(cityblp2[[i]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")
}
layout(matrix(c(1,2,3,4,5,6),ncol=3,nrow=2,byrow=T))
par(mar=c(5,4,3,1),mgp=c(3,1,0),las=1,cex.axis=0.9,cex.lab=1)
plot(cityblp1[[7]],col="blue",axes=T,lab=c(6,5,7), xlab=xlab, ylim=c(min(cityblp2[[i]]$allRRlow),5),
  ylab="RR", ci.arg=list(density=20,angle=-45,col=4), main=names(villes_s)[7])
lines(cityblp2[[7]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")
for (i in 8:12){
#par(mar=c(5,4,3,1),mgp=c(3,1,0),las=1,cex.axis=0.9,cex.lab=1)
plot(cityblp1[[i]],col="blue",axes=T,lab=c(6,5,7), xlab=xlab,
  ylab="RR", ci.arg=list(density=20,angle=-45,col=4), ylim=c(min(cityblp2[[i]]$allRRlow),max(cityblp2[[i]]$allRRhigh)), main=names(villes_s)[i])
lines(cityblp2[[i]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")
}
layout(matrix(c(1,2,3,4,5,6),ncol=3,nrow=2,byrow=T))
i=13
par(mar=c(5,4,3,1),mgp=c(3,1,0),las=1,cex.axis=0.9,cex.lab=1)
plot(cityblp1[[i]],"overall",col="blue",axes=T,lab=c(6,5,7),xlab=xlab,
  ylab="RR", ci.arg=list(density=20,angle=-45,col=4), ylim=c(min(cityblp2[[i]]$allRRlow),4), main=names(villes_s)[i])
lines(cityblp2[[i]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")

i=14
par(mar=c(5,4,3,1),mgp=c(3,1,0),las=1,cex.axis=0.9,cex.lab=1)
plot(cityblp1[[i]],"overall",col="blue",axes=T,lab=c(6,5,7),xlab=xlab,
  ylab="RR", ci.arg=list(density=20,angle=-45,col=4), ylim=c(min(cityblp2[[i]]$allRRlow),2), main=names(villes_s)[i])
lines(cityblp2[[i]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")

i=15
par(mar=c(5,4,3,1),mgp=c(3,1,0),las=1,cex.axis=0.9,cex.lab=1)
plot(cityblp1[[i]],"overall",col="blue",axes=T,lab=c(6,5,7),xlab=xlab,
  ylab="RR", ci.arg=list(density=20,angle=-45,col=4), ylim=c(min(cityblp2[[i]]$allRRlow),6), main=names(villes_s)[i])
lines(cityblp2[[i]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")

par(mar=c(5,4,3,1),mgp=c(3,1,0),las=1,cex.axis=0.9,cex.lab=1)
plot(cityblp1[[16]],col="blue",axes=T,lab=c(6,5,7),xlab=xlab,
  ylab="RR", ci.arg=list(density=20,angle=-45,col=4), ylim=c(0.50, 2.), main=names(villes_s)[16])
lines(cityblp2[[i]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")
for (i in 17:18){
par(mar=c(5,4,3,1),mgp=c(3,1,0),las=1,cex.axis=0.9,cex.lab=1)
plot(cityblp1[[i]],col="blue",axes=T,lab=c(6,5,7),xlab=xlab,
  ylab="RR", ci.arg=list(density=20,angle=-45,col=4), ylim=c(min(cityblp2[[i]]$allRRlow),max(cityblp2[[i]]$allRRhigh)), main=names(villes_s)[i])
lines(cityblp2[[i]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")
}

layout(matrix(c(1,2,3,4,5,6),ncol=3,nrow=2,byrow=T))
par(mar=c(5,4,3,1),mgp=c(3,1,0),las=1,cex.axis=0.9,cex.lab=1)
plot(cityblp1[[19]],col="blue",axes=T,lab=c(6,5,7),xlab=xlab,ylim=c(min(cityblp2[[19]]$allRRlow),max(cityblp2[[19]]$allRRhigh)),
  ylab="RR", main=names(villes_s)[19], ci.arg=list(density=20,angle=-45,col=4))
lines(cityblp2[[19]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")

for (i in 20:21){
par(mar=c(5,4,3,1),mgp=c(3,1,0),las=1,cex.axis=0.9,cex.lab=1)
plot(cityblp1[[i]],col="blue",axes=T,lab=c(6,5,7),xlab=xlab,ylim=c(0.80,2),
  ylab="RR", main=names(villes_s)[i], ci.arg=list(density=20,angle=-45,col=4))
lines(cityblp2[[i]], col="red", ci="area", ci.arg=list(density=20,col=2))
legend("topleft",c("First Period","Second Period")
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=0.7,ncol=1,inset=0.01,bty="n")
}
```

### 2c. Create basis variable for predictions

```{r}
# PREDICTION FOR A GRID OF TEMPERATURE AND LAG VALUES

# OVERALL CUMULATIVE SUMMARY ASSOCIATION FOR MAIN MODEL

model.class <- class(mvall1)
# coeff <- dlnm:::getcoef(mvall2,model.class)
# vcova <- dlnm:::getvcov(mvall2,model.class)
#model.link <- dlnm:::getlink(mvall1,model.class)

# test<-c(coef(mvall1)[[1]], coef(mvall1)[[2]], coef(mvall1)[[3]], coef(mvall1)[[4]])
# vcova<-matrix(ncol=4, nrow=4, dlnm:::getvcov(mvall1,model.class))

cpall1 <- crosspred(bvar_1, coef=dlnm:::getcoef(mvall1,model.class), vcov=dlnm:::getvcov(mvall1,model.class), model.link="log",by=0.1,from=min(tempall_1, na.rm=TRUE),to=max(tempall_1, na.rm=TRUE), cen=median(tempall, na.rm=TRUE))

cpall2 <- crosspred(bvar_2, coef=dlnm:::getcoef(mvall2,model.class), vcov=dlnm:::getvcov(mvall2,model.class), model.link="log",by=0.1,from=min(tempall_2, na.rm=TRUE),to=max(tempall_2, na.rm=TRUE), cen=median(tempall, na.rm=TRUE))

```


### 2d. Create Overall Pooled Predictions

```{r, echo=FALSE}
x<-lapply(villes_s,function(x){x[,c("tempmoy", "day")]})
x1<-list()
x2<-list()

for (i in 1:length(villes_s)){
  x1[[i]]<-x[[i]][which(x[[i]]$day > 31 & x[[i]]$day<77),]
  x2[[i]]<-x[[i]][which(x[[i]]$day > 76 & x[[i]]$day<124),]
  }

names(x1)<-names(villes_s)
names(x2)<-names(villes_s)

tempall1<-rbind(x1[["avignon"]],x1[["douai-lens"]],x1[["bordeaux"]],x1[["clermont"]],x1[["dijon"]],x1[["grenoble"]], x1[["lehavre"]], x1[["lille"]],x1[["lyon"]],x1[["marseille"]], x1[["montpellier"]],x1[["nancy"]],x1[["nantes"]],x1[["nice"]],x1[["paris"]],x1[["rennes"]],x1[["rouen"]],x1[["saint_etienne"]],x1[["strasbourg"]],x1[["toulon"]],x1[["toulouse"]])

tempall2<-rbind(x2[["avignon"]],x2[["douai-lens"]],x2[["bordeaux"]],x2[["clermont"]],x2[["dijon"]],x2[["grenoble"]], x2[["lehavre"]], x2[["lille"]],x2[["lyon"]],x2[["marseille"]], x2[["montpellier"]],x2[["nancy"]],x2[["nantes"]],x2[["nice"]],x2[["paris"]],x2[["rennes"]],x2[["rouen"]],x2[["saint_etienne"]],x2[["strasbourg"]],x2[["toulon"]],x2[["toulouse"]])
```



```{r, echo=FALSE, fig.dim=c(8,8)}

xname="Temperature (˚C)"

layout(matrix(1:3,ncol=1),heights=c(0.8,0.20,0.35))
par(mar=c(0.2,5,2,1),las=1,cex.axis=0.8,cex.lab=1)
plot(cpall1,col="blue",lab=c(6,5,7),axes=F, xlab="Temperature (C)",
  ylab="RR",  ci.arg=list(density=20,angle=-45,col=4), xlim=c(min(xvar_1),max(xvar_2)), ylim=c(0.50,3.5))
lines(cpall2, col="red", ci="area", ci.arg=list(density=20,col=2), xlim=c(min(xvar_1),max(xvar_2)))
legend("topleft",c("First Period \n (I²=1.0%, X² test p-val = 0.8930)","Second Period \n (I²=82.4%, X² test p-val = 0.0000)"), horiz = TRUE
  ,xpd = TRUE,col=c("blue","red"),lwd=2,bg="white"
  ,cex=1.3,ncol=1,inset=0.01,bty="n")
# abline(v=mft[i],lty=1, col="blue")
# abline(v=quantile(villes_s[[i]]$tempmoy,c(0.1,0.75,0.90)),lty=2)
axis(2,at=c(0,0.50, 0.75, 1, 1.25, 1.5, 1.75, 2,2.25, 2.5, 2.75, 3, 3.25, 3.5))
par(mar=c(0.1,5,0.3,1))
hist(tempall1$tempmoy,col=grey(0.95),ylab="Temp Freq\nFirst Period", xlim=c(min(xvar_1),max(xvar_2)),breaks=20, axes=F, main="")
# abline(v=mft[i],lty=1, col="blue")
# abline(v=quantile(villes_s[[i]]$tempmoy,c(0.1,0.75,0.90)),lty=2)
axis(2,at=0:50*100)
par(mar=c(4,5,0.3,1))
hist(tempall2$tempmoy,col=grey(0.95),ylab="Temp Freq\nSecond Period",xlim=c(min(xvar_1),max(xvar_2)), breaks=20, main="", xlab=xname)
axis(2,at=0:50*100)


```



