---
title: "Effect of different Heat wave timing on cardiovascular and respiratory mortality in France - Analysis with categorical variable for Heat wave order"
author: "Anna Alari and Noemie Letellier"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE)
```


```{r, echo=FALSE, warning = FALSE, message=FALSE}
library(xlsx)
library(Hmisc)
library(lubridate)
library(effects)
library(ggplot2)
library(prettyR)
library(segmented)
library(splines)
library(mgcViz)
library(ggeffects)
library(devtools)
library(zoo)
library(mvmeta)
library(dlnm)
library(knitr)
library(kableExtra)
library(tidyverse)
library("writexl")
library(metafor)
library(forestplot)
library(hrbrthemes)
library(tidyverse)
library(ggridges)
library(viridis)
library(ggpubr)
library(R.utils)
library(meta)
library(jtools)
library(huxtable)
library(gdata)
```



```{r}
load("C:/Users/aalari/Dropbox/Noemie/FInal Analysis - SpF + CepiDC/villes_s.RData")

```



The aim of the following analysis is to estimate whether heat waves occuring at different timing during the summer may have different effect on mortality. 

Heat wave variable was created according to the Meteo France definition for extreme weather events. 
Heat waves were defined as periods where the mean daily temperature exceeded the 97.5th percentile of the local (within each urban agglomeration) mean temperature distribution over the entire year (*initial threshold*) for at least three consecutive days, and for which at least one day recorded a mean daily temperature above the 99.5th percentile of the local temperature distribution for the entire year  (*peak threshold*). For references, see Soubeyroux et al. 2016 (DOI: 10.4267/2042/60704) and Pascal et al. 2021 (DOI: https://doi.org/10.1016/j.atmosenv.2021.118249). 






We still have 4 heat wave episodes in a summer in some cities: Grenoble, Lyon, Montpellier and Saint Entienne in 2003, Nancy in 2015. 
3 Heat waves episodes in Marseille and Lyon in 2015 

## Model
We just put in the model the "order heat wave" variable, which allow to consider mortality risk for non heat-wave days compared to mortality risk during heat-wave days, and allow also the risk of mortality to differ by heat wave timing (inspired by Anderson and Bell, 2011).

- The category "0" will be taken as the reference category in the model 
- the category 1 is for first heat wave of the season
- the category 2 is for heat waves other than the first




### Cardiovascular Deaths
```{r, message=FALSE}
m.outcome4bis<-list()
v.coeffHW1<-c()
v.sterrHW1<-c()
v.coeffHW2<-c()
v.sterrHW2<-c()
resultsHW1<-matrix(NA,nrow = 21,ncol=4)
colnames(resultsHW1)<-c("city","HW1","HW1_2.5","HW1_97.5")
resultsHW1[,1]<-names(villes_s)

resultsHW2<-matrix(NA,nrow = 21,ncol=4)
colnames(resultsHW2)<-c("city","HW2","HW2_2.5","HW2_97.5")
resultsHW2[,1]<-names(villes_s)


for (i in 1:length(villes_s)){
m.outcome4bis[[i]]<-glm(cv_tot~orderhw+annee+Jours+Vacances,data=villes_s[[i]],family=quasipoisson)
v.coeffHW1[i]<-m.outcome4bis[[i]]$coefficients[2]
v.sterrHW1[i]<-summary(m.outcome4bis[[i]])$coefficients[2, 2]
v.coeffHW2[i]<-m.outcome4bis[[i]]$coefficients[3]
v.sterrHW2[i]<-summary(m.outcome4bis[[i]])$coefficients[3, 2]
resultsHW1[i,2]<-m.outcome4bis[[i]]$coefficients[2]
resultsHW1[i,3:4]<-confint.default(m.outcome4bis[[i]])[2,]
resultsHW2[i,2]<-m.outcome4bis[[i]]$coefficients[3]
resultsHW2[i,3:4]<-confint.default(m.outcome4bis[[i]])[3,]
}

names(m.outcome4bis)<-names(villes_s)
```

### Results per city 
<details>
  <summary> Avignon </summary>
```{r}
summ(m.outcome4bis[[1]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> BM </summary>
```{r}
summ(m.outcome4bis[[2]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 


<details>
  <summary> Bordeaux </summary>
```{r}
summ(m.outcome4bis[[3]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 


<details>
  <summary> Clermont-Ferrand </summary>
```{r}
summ(m.outcome4bis[[4]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Dijon </summary>
```{r}
summ(m.outcome4bis[[5]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Grenoble </summary>
```{r}
summ(m.outcome4bis[[6]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> La Havre </summary>
```{r}
summ(m.outcome4bis[[7]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Lille </summary>
```{r}
summ(m.outcome4bis[[8]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Lyon </summary>
```{r}
summ(m.outcome4bis[[9]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Marseille </summary>
```{r}
summ(m.outcome4bis[[10]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Montpellier </summary>
```{r}
summ(m.outcome4bis[[11]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Nancy </summary>
```{r}
summ(m.outcome4bis[[12]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Nantes </summary>
```{r}
summ(m.outcome4bis[[13]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Nice </summary>
```{r}
summ(m.outcome4bis[[14]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Paris </summary>
```{r}
summ(m.outcome4bis[[15]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Rennes </summary>
```{r}
summ(m.outcome4bis[[16]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Rouen </summary>
```{r}
summ(m.outcome4bis[[17]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 


<details>
  <summary> Saint-Etienne </summary>
```{r}
summ(m.outcome4bis[[18]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 


<details>
  <summary> Strasbourg </summary>
```{r}
summ(m.outcome4bis[[19]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Toulon </summary>
```{r}
summ(m.outcome4bis[[20]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Toulouse </summary>
```{r}
summ(m.outcome4bis[[21]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

### Meta-analysis: {.tabset .tabset-fade}

#### For First Heat Weave Category:
```{r, echo=FALSE, fig.width=7, fig.height=7, fig.align = "center"}
metaHW1<-rma(v.coeffHW1,sei=v.sterrHW1)
summary(metaHW1)

forest(metaHW1,transf = exp, slab = names(villes_s),refline=1,xlab="RR First Heat Wave", header="City")
```

#### For Second or higher Heat Waves:
```{r, echo=FALSE, fig.width=7, fig.height=7, fig.align = "center"}
metaHW2<-rma(v.coeffHW2,sei=v.sterrHW2)
summary(metaHW2)

forest(metaHW2,transf = exp, slab = names(villes_s),refline=1,xlab="RR Second Heat Wave", header="City")

```

#### Comparing First and Second or higher Heat Wave effect:


```{r, echo=FALSE, fig.width=8, fig.height=8, fig.align = "center"}

metaHW1bis<-metagen(TE=v.coeffHW1,seTE=v.sterrHW1)
metaHW2bis<-metagen(TE=v.coeffHW2,seTE=v.sterrHW2)

resultsHW1<-as.data.frame(resultsHW1)
resultsHW2<-as.data.frame(resultsHW2)

resultsHW1[,1]<-as.character(resultsHW1[,1])
resultsHW2[,1]<-as.character(resultsHW2[,1])

for (i in 2:4){
resultsHW1[,i]<-as.numeric(as.character(resultsHW1[,i]))
resultsHW2[,i]<-as.numeric(as.character(resultsHW2[,i]))
}

resultsHW1[,2:4]<-exp(resultsHW1[,2:4])
resultsHW2[,2:4]<-exp(resultsHW2[,2:4])

resultsHW1$city<-as.factor(as.character(resultsHW1$city))
resultsHW2$city<-as.factor(as.character(resultsHW2$city))

order<-c("bordeaux","lehavre","nantes","rennes","rouen","clermont","dijon","grenoble","lyon","nancy","saint_etienne", "strasbourg","BM","lille", "paris","toulouse","avignon","marseille","montpellier","nice","toulon")

resultsHW1$city <- reorder.factor(resultsHW1$city, new.order=order) 
resultsHW2$city <- reorder.factor(resultsHW2$city, new.order=order) 

resultsHW1$city<-factor(resultsHW1$city,levels(resultsHW1$city), labels=c("Bordeaux","Le Havre","Nantes","Rennes","Rouen","Clermont-Ferrant","Dijon","Grenoble","Lyon","Nancy","Saint-Etienne", "Strasbourg","Douai-Lens","Lille", "Paris","Toulouse","Avignon","Marseille","Montpellier","Nice","Toulon")) 

resultsHW2$city<-factor(resultsHW2$city,levels(resultsHW2$city), labels=c("Bordeaux","Le Havre","Nantes","Rennes","Rouen","Clermont-Ferrant","Dijon","Grenoble","Lyon","Nancy","Saint-Etienne", "Strasbourg","Douai-Lens","Lille", "Paris","Toulouse","Avignon","Marseille","Montpellier","Nice","Toulon")) 

resultsHW1 <-resultsHW1[order(resultsHW1$city),]
resultsHW2 <- resultsHW2[order(resultsHW2$city),]

resultsHW1$city<-as.character(resultsHW1$city)
resultsHW2$city<-as.character(resultsHW2$city)




forestplot(resultsHW1[,1],legend = c("First Heat Wave \n Pooled RR: 1.30 [1.17, 1.45] \n (I²=78.77%, X² test p-val < .0001)", "Second or Higher Heat Wave \n Pooled RR: 1.38 [1.23, 1.53] \n (I²=59.94%, X² test p-val < 0.0001)"), 
           mean = cbind(resultsHW1[,2], resultsHW2[,2]),
           lower = cbind(resultsHW1[,3], resultsHW2[,3]),
           upper = cbind(resultsHW1[,4], resultsHW2[,4]),
           col = fpColors(box = c("blue", "darkred")),
           xlab = "RR", zero = 1,lty.ci = c(1, 2))


```


### Respiratory Deaths
```{r, message=FALSE}
m.outcome4bis<-list()
v.coeffHW1<-c()
v.sterrHW1<-c()
v.coeffHW2<-c()
v.sterrHW2<-c()
resultsHW1<-matrix(NA,nrow = 21,ncol=4)
colnames(resultsHW1)<-c("city","HW1","HW1_2.5","HW1_97.5")
resultsHW1[,1]<-names(villes_s)

resultsHW2<-matrix(NA,nrow = 21,ncol=4)
colnames(resultsHW2)<-c("city","HW2","HW2_2.5","HW2_97.5")
resultsHW2[,1]<-names(villes_s)


for (i in 1:length(villes_s)){
m.outcome4bis[[i]]<-glm(respi_tot~orderhw+annee+Jours+Vacances,data=villes_s[[i]],family=quasipoisson)
v.coeffHW1[i]<-m.outcome4bis[[i]]$coefficients[2]
v.sterrHW1[i]<-summary(m.outcome4bis[[i]])$coefficients[2, 2]
v.coeffHW2[i]<-m.outcome4bis[[i]]$coefficients[3]
v.sterrHW2[i]<-summary(m.outcome4bis[[i]])$coefficients[3, 2]
resultsHW1[i,2]<-m.outcome4bis[[i]]$coefficients[2]
resultsHW1[i,3:4]<-confint.default(m.outcome4bis[[i]])[2,]
resultsHW2[i,2]<-m.outcome4bis[[i]]$coefficients[3]
resultsHW2[i,3:4]<-confint.default(m.outcome4bis[[i]])[3,]
}

names(m.outcome4bis)<-names(villes_s)
```

### Results per city 
<details>
  <summary> Avignon </summary>
```{r}
summ(m.outcome4bis[[1]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> BM </summary>
```{r}
summ(m.outcome4bis[[2]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 


<details>
  <summary> Bordeaux </summary>
```{r}
summ(m.outcome4bis[[3]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 


<details>
  <summary> Clermont-Ferrand </summary>
```{r}
summ(m.outcome4bis[[4]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Dijon </summary>
```{r}
summ(m.outcome4bis[[5]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Grenoble </summary>
```{r}
summ(m.outcome4bis[[6]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> La Havre </summary>
```{r}
summ(m.outcome4bis[[7]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Lille </summary>
```{r}
summ(m.outcome4bis[[8]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Lyon </summary>
```{r}
summ(m.outcome4bis[[9]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Marseille </summary>
```{r}
summ(m.outcome4bis[[10]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Montpellier </summary>
```{r}
summ(m.outcome4bis[[11]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Nancy </summary>
```{r}
summ(m.outcome4bis[[12]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Nantes </summary>
```{r}
summ(m.outcome4bis[[13]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Nice </summary>
```{r}
summ(m.outcome4bis[[14]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Paris </summary>
```{r}
summ(m.outcome4bis[[15]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Rennes </summary>
```{r}
summ(m.outcome4bis[[16]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Rouen </summary>
```{r}
summ(m.outcome4bis[[17]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 


<details>
  <summary> Saint-Etienne </summary>
```{r}
summ(m.outcome4bis[[18]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 


<details>
  <summary> Strasbourg </summary>
```{r}
summ(m.outcome4bis[[19]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Toulon </summary>
```{r}
summ(m.outcome4bis[[20]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 

<details>
  <summary> Toulouse </summary>
```{r}
summ(m.outcome4bis[[21]], exp = TRUE, confint = TRUE, digits = 3)
```
</details> 


I have to exclude Clermont Ferrand from the results because of estimation problems. 

### Meta-analysis: {.tabset .tabset-fade}

#### For First Heat Weave Category:
```{r, echo=FALSE, fig.width=7, fig.height=7, fig.align = "center"}
v.coeffHW1<-v.coeffHW1[-4]
v.sterrHW1<-v.sterrHW1[-4]

metaHW1<-rma(v.coeffHW1,sei=v.sterrHW1)
summary(metaHW1)

forest(metaHW1,transf = exp, slab = names(villes_s[-4]),refline=1,xlab="RR First Heat Wave", header="City")
```

#### For Second or Higher Heat Waves:
```{r, echo=FALSE, fig.width=7, fig.height=7, fig.align = "center"}
v.coeffHW2<-v.coeffHW2[-4]
v.sterrHW2<-v.sterrHW2[-4]

metaHW2<-rma(v.coeffHW2,sei=v.sterrHW2)
summary(metaHW2)

forest(metaHW2,transf = exp, slab = names(villes_s[-4]),refline=1,xlab="RR Second Heat Wave", header="City")

```

#### Comparing First with Others Heat Wave effect:


```{r, fig.width=8, fig.height=8, fig.align = "center", echo=FALSE}
metaHW1bis<-metagen(TE=v.coeffHW1,seTE=v.sterrHW1)
metaHW2bis<-metagen(TE=v.coeffHW2,seTE=v.sterrHW2)

resultsHW1<-as.data.frame(resultsHW1[-4,])
resultsHW2<-as.data.frame(resultsHW2[-4,])

resultsHW1[,1]<-as.character(resultsHW1[,1])
resultsHW2[,1]<-as.character(resultsHW2[,1])


for (i in 2:4){
resultsHW1[,i]<-as.numeric(as.character(resultsHW1[,i]))
resultsHW2[,i]<-as.numeric(as.character(resultsHW2[,i]))
}

resultsHW1[,2:4]<-exp(resultsHW1[,2:4])
resultsHW2[,2:4]<-exp(resultsHW2[,2:4])

resultsHW1$city<-as.factor(as.character(resultsHW1$city))
resultsHW2$city<-as.factor(as.character(resultsHW2$city))

order<-c("bordeaux","lehavre","nantes","rennes","rouen","clermont","dijon","grenoble","lyon","nancy","saint_etienne", "strasbourg","BM","lille", "paris","toulouse","avignon","marseille","montpellier","nice","toulon")

resultsHW1$city <- reorder.factor(resultsHW1$city, new.order=order) 
resultsHW2$city <- reorder.factor(resultsHW2$city, new.order=order) 

resultsHW1$city<-factor(resultsHW1$city,levels(resultsHW1$city), labels=c("Bordeaux","Le Havre","Nantes","Rennes","Rouen","Clermont-Ferrant","Dijon","Grenoble","Lyon","Nancy","Saint-Etienne", "Strasbourg","Douai-Lens","Lille", "Paris","Toulouse","Avignon","Marseille","Montpellier","Nice","Toulon")) 

resultsHW2$city<-factor(resultsHW2$city,levels(resultsHW2$city), labels=c("Bordeaux","Le Havre","Nantes","Rennes","Rouen","Clermont-Ferrant","Dijon","Grenoble","Lyon","Nancy","Saint-Etienne", "Strasbourg","Douai-Lens","Lille", "Paris","Toulouse","Avignon","Marseille","Montpellier","Nice","Toulon")) 

resultsHW1 <-resultsHW1[order(resultsHW1$city),]
resultsHW2 <- resultsHW2[order(resultsHW2$city),]

resultsHW1$city<-as.character(resultsHW1$city)
resultsHW2$city<-as.character(resultsHW2$city)


forestplot(resultsHW1[,1],legend = c("First Heat Wave \n Pooled RR: 1.56 [1.33, 1.83] \n (I²=55.22%, X² test p-val < .0001)", "Second or Higher Heat Wave \n Pooled RR: 1.74 [1.45, 2.08] \n (I²=46.91%, X² test p-val = 0.0164)"), 
           mean = cbind(resultsHW1[,2], resultsHW2[,2]),
           lower = cbind(resultsHW1[,3], resultsHW2[,3]),
           upper = cbind(resultsHW1[,4], resultsHW2[,4]),
           col = fpColors(box = c("blue", "darkred")),
           xlab = "RR", zero = 1,lty.ci = c(1, 2))



```


